TextGrids

### 2020-12-30 osf/comps/dataset/raw/README.Rmd
use osfr to manage the OSF repo

---
title: "Dataset & Materials"
output:
  github_document:
    html_preview: false
---

@@

This directory contains 3 subdirectories: `Materials/`, `Raw data/`, and `TextGrids/`.
See the `README.md` files of each individual directory for more information about the contents.

@@

```{r data_files, include=TRUE}
osf_ls_files(data_comp) %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

---
title: "Raw data"
output:
  github_document:
    html_preview: false
---

@@

This directory contains `.wav` files of the participants’ production from the experiment.

@@

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "Raw data") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

### 2020-12-30 osf/comps/dataset/textgrids/README.Rmd
use osfr to manage the OSF repo

---
title: "Raw data"
output:
  github_document:
    html_preview: false
---

@@

This directory contains `.wav` files of the participants’ production from the experiment.

@@

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "Raw data") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

---
title: "TextGrids"
output:
  github_document:
    html_preview: false
---

@@

This directory contains Praat's `.TextGrid` files corresponding to the `.wav` files in `Raw data/`.

@@

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "TextGrids") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```
